Article Title

### 2013-09-06 sections/Results.tex
included figure5.

\textbf{Figure 4.}{ 
The fitting performance of regularized covariance estimators on two-photon recording. 
}\label{fig:04}

\textbf{Figure 5.}{ 
Fitting performance of regularized covariance estimators on 24 datasets two-photon recordinngs.
}\label{fig:05}

\textbf{Figure 6.}{
The depiction of the 3D arrangement of the non-zero partial correlations between pairs of neurons.
}\label{fig:06}

>>>>

\begin{figure}[htp]
\centering
\includegraphics[width=0.5\textwidth]{figures/placeholder.pdf}
\caption{
Cross-validated performance of covariance estimators in one two-photon recording.
}\label{fig:04}
\end{figure}

\begin{figure}[htp]
\centering
\includegraphics[width=1.0\textwidth]{figures/Figure5.pdf}
\caption{
Cross-validated comparisons of the five covariance estimators on 31 two-photon recordings. 
}\label{fig:05}
\end{figure}

\begin{figure}[htp]
\centering
\includegraphics[width=0.5\textwidth]{figures/placeholder}
\caption{
The depiction of the 3D arrangement of the non-zero partial correlations between pairs of neurons.
}\label{fig:06}
\end{figure}
